---
title: "Baseball data: Learning Activity 4"
format: pdf
editor: visual
---

## Background

This activity uses the **baseball** dataset (available in the *SDAResources* package). The dataset contains statistics on **797 baseball players** from the rosters of all major league teams in November 2004 (Forman, 2004).

You will treat this file as a **population** and draw samples from it using stratified random sampling.

## Getting Started

Loading the dataset and the R packages. Visit the solutions for learning activity 3 on R introductions. No new R functions will be needed for this activity. 

```{r,message=FALSE}
#| label: setup
# Uncomment the install.packages("SDAResources") line to install the package. 
# Comment it back after you install the package :) 
# install.packages("SDAResources") 
library(SDAResources)
library(dplyr)

data(baseball)         

```

## Exercise 1: Stratified random sample

Take a stratified random sample of 150 players from the population, using proportional allocation with the different teams as strata. 

```{r}
#Include your code here

```

Describe how you selected the sample here: 







## Exercise 2: Inference for the population proportion

Estimate the population proportion of players who are pitchers and give a 95\% confidence interval, using your stratified sample. Do this manually using the formulas from lecture/the textbook — do not rely on pre-built R functions except for `mean()`, `sd()`, `qnorm(0.975)`, or `qt(0.975, df = n - 1)`, which give you the 97.5th quantile from a standard normal distribution and a t-distribution with $n - 1$ degrees of freedom, respectively.

```{r}
## Include your code here




```

Give the estimate and the 95% CI and interpret them here:







## Exercise 3: Inference for the population mean

Estimate the population mean of `logsal` and give a 95% CI, using your stratified sample. Recall from activity 3 that `logsal` is the logarithm of `salary`. 

Do this manually using the formulas from lecture/the textbook — do not rely on pre-built R functions except for `mean()`, `sd()`, `qnorm(0.975)`, or `qt(0.975, df = n - 1)`, which give you the 97.5th quantile from a standard normal distribution and a t-distribution with $n - 1$ degrees of freedom, respectively.

```{r}
# Include your code here







```

Give the estimate and the 95% CI and interpret them here:







## Exercise 4
How do your estimates compare with those of Learning activity 3?









## Exercise 5
Examine the sample variance in each stratum. Do you think optimal allocation would be worthwhile for this problem? 

```{r}
## Use this for code





```





## Exercise 6
Using the sample variances from Exercise 5 to estimate the population stratum variances, determine the optimal allocation for a sample in which the cost is the same in each stratum and the total sample size is 150. How much does the optimal allocation differ from the proportional allocation? 









